Codebook
========
Codebook was generated on `r as.character(Sys.time())` during the same process that
generated the dataset. See `run_analysis.md` or `run_analysis.html` for details on
dataset creation.

Variable list and descriptions
--------------------------------------------------------------------
Variable name             | Description
--------------------------|-----------------------------------------
subject                   | who is the test/trial subject
test                      | which of six test modes
t/fBodyAcc-mean()-X,Y,Z   | Feature: Acceleration signal, Body
tGravityAcc-mean()-X,Y,Z  | Feature: Acceleration signal, Gravity
tBodyAccJerk-mean()-X,Y,Z | Feature: Jerk signal
tBodyGyro-mean()-X,Y,Z    | Feature: Measuring instrument, Gyroscope
t/fBodyAcc-sd()-X,Y,Z     | Feature: as above, SD
tGravityAcc-sd()-X,Y,Z    | Feature: as above, 
tBodyAccJerk-sd()-X,Y,Z   | Feature: as above
tBodyGyro-sd()-X,Y,Z      | Feature: as above
pAvg                      | average for all subjects with a feature
mAvg                      | average within one test, one subject

Dataset structure
-----------------
```{r}
str(pTidy)
```
List the key variables in the data table
----------------------------------------
```{r}
fTable[xr,2]
```
Show a few rows of the dataset
------------------------------
```{r}
head(pTidy)
```
Summary of variables
--------------------
```{r}
summary(pTidy)
```
Save to file tidy.csv
------------
